Engineering the Servo Web Browser Engine using Rust

### 2015-10-23 icse16-servo/browsers.tex
Small edits to parsing. Explain what a flow tree is better.

A URL identifies a resource to load.
This resource usually consists of HTML, which is then parsed and typically turned into a Document Object
Model (DOM) tree.
From a programming languages standpoint, there are several interesting aspects of the parser design
for HTML.
First, though the specification allows the browser to abort on a parse error,\footnote{\url{https://html.spec.whatwg.org/multipage/#parsing}}
in practice browsers follow the recovery algorithms described in that specification precisely so that
even ill-formed HTML will be handled in an interoperable way across all browsers.
Second, due to the presence of the \lstinline[language=HTML]{<script>} tag, the token stream can be modified
during operation.
For example, the below example that injects an open tag for the header and comment blocks works in all modern browsers.
\begin{lstlisting}[language=HTML]
<html>
  <script>
  document.write("<h");
  </script>1>
  This is a h1 title

  <script>
  document.write("<!-");
  </script>-
  This is commented
  -->
</html>
\end{lstlisting}
This requires parsing to pause until JavaScript code has run to completion.
But, since resource loading is such a large factor in the latency of loading many webpages (particularly on mobile),
all modern parsers also perform speculative token stream scanning and prefetch of resources likely to be required~\cite{browsers-slow-smartphones}.

@@

After constructing the DOM, the browser uses the styling information in linked
CSS files and in the HTML to compute a styled tree of flows and fragments,
called the \emph{flow tree} in Servo.
This process can create many more flows than previously existed in the DOM ---
for example, when a list item is styled to have an associated counter glyph.

>>>>

A URL identifies a resource to load.
This resource usually consists of HTML, which is then parsed and typically turned into a Document Object
Model (DOM) tree.
From an implementation standpoint, there are two interesting aspects of the parser design
for HTML.
First, though the specification allows the browser to abort on a parse error,\footnote{\url{https://html.spec.whatwg.org/multipage/#parsing}}
in practice browsers follow the recovery algorithms described in that specification precisely so that
even ill-formed HTML will be handled in an interoperable way across all browsers.
Second, due to the presence of the \lstinline[language=HTML]{<script>} tag, the token stream can be modified
during operation.
For example, the below example that injects an open tag for the header and comment blocks works in all modern browsers.
\begin{lstlisting}[language=HTML]
<html>
  <script>
  document.write("<h");
  </script>1>
  This is a h1 title

  <script>
  document.write("<!-");
  </script>-
  This is commented
  -->
</html>
\end{lstlisting}
This requires parsing to pause until JavaScript code has run to completion.
But since resource loading is such a large factor in the latency of loading many webpages,
all modern parsers also perform speculative token stream scanning and prefetch of resources likely to be required~\cite{browsers-slow-smartphones}.

@@

After constructing the DOM, the browser uses the styling information in linked
CSS files and in the HTML to compute a styled tree of flows and fragments.
This \emph{flow tree}, as it is named in Servo, describes the layout of DOM elements on the page,
and may contain many more flows than previously existed in the DOM.
For example, when a list item is styled to have an associated bullet, that bullet
will itself be represented in the flow tree, though it is not part of the DOM.
